---
title: "Math"
theme: Berlin
output:
  beamer_presentation: default
  theme: "Berkeley"

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(fig.width=8, fig.height=5) 
```

## Why?

+ Business school was upset that "Students were not learning anything in EC201/202"
+ Showed with a test of business students
+ The questions they missed were not because of econ but math.
+ Tested in EC201/202
    + 25% can't add fractions
    + 50% can't solve or graph linear equation
    + 75% can't solve system of two equations and two unknowns
    
This is all from 9th grade or earlier.

## But ... But ...

+ We can draw graphs but without the math intuition, its meaningless.
+ "But I understand the theory".  
+ "When will I use this?"
    + to calculate your grade
    + in your business courses  $Payment = P \frac{i(1+i)^n}{(1+i)^n - 1}$
+ The computer does that for me.
    + Yes it does until you get to a certain level
    + Then you don't know enough to make the next step or find the software that will do it for you.
    
    
    
    
    
    
## Add some fractions

$$\frac{1}{2} + \frac{1}{4} = $$


## Another One

$$\frac{2}{3} + \frac{3}{4} = $$

## Multiply Fractions

$$\frac{2}{3} ~ \frac{3}{5}= $$

## Area of a rectangle

```{r Rectangle, echo=FALSE, fig.cap='Rectangle',  fig.pos='!H', message=FALSE, warning=FALSE}

library(ggplot2)
library(data.table)

Sides <- sample(2:6,2)

dt.rectangle <- data.table(group = c(1,1,1,1), polygon.x = c(2,2 + Sides[1], 2+ Sides[1], 2 ), polygon.y = c(2,2,2+ + Sides[2],2 + Sides[2]))

p <- ggplot()
p <- p + geom_polygon(
            data = dt.rectangle
            ,aes(
                x=polygon.x
                ,y=polygon.y
                ,group=group
            )
        ) + theme_minimal() + xlim(0,8) + ylim(0,8) + xlab("") + ylab("") 

p
```


## Triangle


```{r Triangle, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='Triangle', fig.pos ='!H'}

library(ggplot2)
library(data.table)

Type <- list(list(2,3), list(1,4))
Orient <- sample(unlist(sample(Type, 1)),2)

dt.triangle <- data.table(group = c(1,1,1), polygon.x = c(2,2 + Orient[1],2), polygon.y = c(1,1,1 + Orient[2]))

p <- ggplot()
p <- p + geom_polygon(
            data = dt.triangle
            ,aes(
                x=polygon.x
                ,y=polygon.y
                ,group=group
            )
        ) + theme_minimal() + xlim(0,6) + ylim(0,6) + xlab("") + ylab("")

p
```


## Percent Change

What is the percent increase from 60 to 63?

## Plot a Line 

Plot $$y = -1 + 2 x$$

## Solve for p

$$P = 2 + \frac{3}{4} P$$

## What is the slope of this line?

$$ 5 y + 3 x = 2$$

## Solve for P and Q


$$
p-9 = 3(q-3)
$$

$$
p =20 -2 q
$$
